---
output:
  html_document:
    number_sections: FALSE
    includes:
      in_header: itn_favicon.html
css: css/ITN_style.css
---

```{r, echo=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_itn_header.md",
  tag_replacement = list(
    "{TITLE}" = "Chairing Sessions", 
    "{SUBTITLE}" =  "Roles and Goals",
    "{PATH_TO_PNG}" = "https://raw.githubusercontent.com/jhudsl/cheatsheets/refs/heads/main/pngs/chairing.png"
    ))
```

## Responsibilities

A session chair at a scientific conferences:

- Introduces topics and speakers
- Facilitates questions
- Manages time

<hr>

## Tasks Ahead of Time

<input type="checkbox">  Meet with session speakers 

1. <input type="checkbox">  Check name pronunciation 

1. <input type="checkbox">  Check affiliation 

1. <input type="checkbox">  Remind speakers about declaring conflicts

1. <input type="checkbox">  Explain timing plan

1. <input type="checkbox">  Perform technical checks

1. <input type="checkbox">  If virtual confirm communication plan for day of
(e.g. slack channel)

<input type="checkbox">  Review speakers plans for speaking to come up with possible questions

<input type="checkbox">  Remind session speakers 

1. <input type="checkbox">  Request speakers to come early day of event

1. <input type="checkbox">  Remind session speakers **one week** before 

1. <input type="checkbox">  Remind session speakers **one day** before 

<hr>

<center>
:::warning

If you are co-hosting, make sure you both are aligned on who is responsible for each task.
:::
</center>



## Tasks Day of Event

<input type="checkbox">  Show up early to check systems and check in with speakers

<input type="checkbox">  Give a short summary of the session
(e.g., "This session is about Topic X and will have Y speakers")

<input type="checkbox"> Provide housekeeping announcements 
(e.g., break time, voting, etc.)

<input type="checkbox">  Introduce speakers
(name, role, institution, talk title)
<input type="checkbox">  Watch the time to ensure schedule is maintained

<input type="checkbox">  Ask the audience for questions
1. <input type="checkbox"> if no questions, ask your own
<hr>

<center>
:::warning

If you are co-hosting, make sure you both are aligned on who is responsible for each task.
:::
</center>


## Possible Challenges

Speakers may speak too long

1. <input type="checkbox"> Notify speakers of time limits (5 min left, 1 min left) 
1. <input type="checkbox"> Interrupt the speaker if needed
1. <input type="checkbox"> Shorten question sessions as needed 
1. <input type="checkbox"> Adjust subsequent speaker times if needed 

People may ask too many questions

1. <input type="checkbox"> Interrupt and ask for the discussion to happen later

People may not have questions

1. <input type="checkbox"> Come up with your own question(s) to give people time to think of additional questions


```{r, echo=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_itn_footer.md",
  tag_replacement = list(
    "{AUTHORS}" = "Content for this cheatsheet came from Carrie Wright, Kate Isaac, and Sean Davis"
    ))
```
