---
format:
  html:
    toc: true
    toc-depth: 4
    toc-location: left
css: styles.css
---

# Want to contribute to the cheatsheets?

<div class="banner_color">
Read this guide before opening a pull request.
</div>

Please review our [Contributor Covenant Code of Conduct](https://github.com/ottrproject/OTTR_Template/blob/main/code_of_conduct.md) before contributing.

## Making a New Cheatsheet

Create a `.Rmd` or `.md` file at the top level of the repository. **GitHub Actions will automatically render it as a PNG saved to the `docs` folder.**

### 1. Choose a Style

Specify respective style in the yaml header: 

**OTTR style:**

```{yaml}
---
output: html_document
css: css/OTTR_style.css
---
```

or 

**ITN style:**

```{yaml}
---
output:
  html_document:
    number_sections: false
css: css/ITN_style.css
---
```

### 2. Add a Header Chunk

All cheatsheets should start with either `chunk/create_ottr_header.md` or `chunk/create_itn_header/md`. Specify the title, subtitle, and path to the PNG image.

Example:

```{r, eval=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_itn_header.md",
  tag_replacement = list(
    "{TITLE}"       = "Your Title",
    "{SUBTITLE}"    = "Your Subtitle",
    "{PATH_TO_PNG}" = "path-to-image.png"
  ))
```

### 3. Add the corresponding PNG file

Each cheatsheet needs a corresponding PNG for the header and gallery. GitHub Actions will automatically render a PNG when you create your cheatsheet. 

Example path:

```
https://raw.githubusercontent.com/ottrproject/cheatsheets/refs/heads/main/pngs/attending_conferences.png
```

### 4. Add a Footer Chunk

Every cheatsheet must end with a footer chunk. Use it to credit authors and contributors.

Example with OTTR footer:

```{r eval=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_ottr_footer.md",
  tag_replacement = list(
    "{AUTHORS}" = "[Author name] wrote the content. [Contributor name] reviewed and improved the cheatsheet."
  ))
```


## Reusing Content with Chunks

If text will appear more than once, put it in a `.md` file inside the `chunks` folder. Use `{PLACEHOLDER}` tags for variable content (not regex). 

Chunks are especially useful for:

- Headers and footers
- Setup instructions
- Repeated GitHub workflow steps
- Standard reference sections

**Example call:**

```{r eval=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_itn_header.md",
  tag_replacement = list(
    "{TITLE}"       = "Attending Conferences",
    "{SUBTITLE}"    = "Helpful Tips",
    "{PATH_TO_PNG}" = "https://raw.githubusercontent.com/ottrproject/cheatsheets/refs/heads/main/pngs/attending_conferences.png"
  ))
```

### Getting icons

| Icon | Output | Code |
|---|---|---|
| Actions | `r config::get("actions")` | `` `r config::get("actions")` `` |
| Copy | `r config::get("copy")` | `` `r config::get("copy")` `` |
| Collaborate | `r config::get("collab")` | `` `r config::get("collab")` `` |
| Develop | `r config::get("dev")` | `` `r config::get("dev")` `` |
| Edit | `r config::get("edit")` | `` `r config::get("edit")` `` |
| Pages | `r config::get("pages")` | `` `r config::get("pages")` `` |
| Token | `r config::get("token")` | `` `r config::get("token")` `` |
| Profile | `r config::get("profile")` | `` `r config::get("profile")` `` |
| Pull Request | `r config::get("PR")` | `` `r config::get("PR")` `` |
| Search | `r config::get("search")` | `` `r config::get("search")` `` |
| Secrets | `r config::get("secrets")` | `` `r config::get("secrets")` `` |
| Settings | `r config::get("settings")` | `` `r config::get("settings")` `` |


## Adding Cheatsheets to the Main Gallery

Update `gallery.yml` with your cheatsheet's information under the appropriate category:

- [Conferences & Engagement](https://www.ottrproject.org/cheatsheets/#conferences-engagement)
- [Research & Software Development](https://www.ottrproject.org/cheatsheets/#research-software-development)
- [OTTR](https://www.ottrproject.org/cheatsheets/#ottr)

Example: 

```yml
- title: Google Analytics Integration
  href: https://ottrproject.org/cheatsheets/google_analytics.html
  code: https://github.com/ottrproject/cheatsheets/blob/main/google_analytics.Rmd
  thumbnail: pngs/google_analytics.png
```

Make sure to check the render of index.Qmd! 

## Contributor Checklist

- [ ] Content is clear, concise, and easy to follow
- [ ] Cheatsheet file is at the top level of the repository
- [ ] YAML header uses the correct style
- [ ] Cheatsheet starts with the correct header chunk
- [ ] Cheatsheet ends with the correct footer chunk
- [ ] Reusable content has been moved to `chunks` where appropriate
- [ ] Links and image paths are correct
- [ ] Cheatsheet has been added to `gallery.yml`
- [ ] Main page render has been checked
