---
output:
  html_document:
    includes:
      in_header: ottr_favicon.html
css: css/OTTR_style.css
---

```{r, echo=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_ottr_header.md",
  tag_replacement = list(
    "{TITLE}" = "OTTR Website Style",
    "{SUBTITLE}" = "Customizing Colors & Style",
    "{PATH_TO_PNG}" = "https://github.com/ottrproject/cheatsheets/blob/main/pngs/ottr_website_style.png?raw=true"
  ))
```

<p class="comment">
<em>Websites look and are configured differently from courses. Use this cheat sheet for an OTTR website; course style instructions are not interchangeable.</em>
</p>

## Website Style Files

An OTTR website has one color configuration file: `assets/style_config_default.css`. Unlike an OTTR course, it does **not** have `style_config_custom.css`.

Use `style_config_default.css` to customize website color variables. Commit the change on a new branch and check the pull request preview.

## Customize Website Colors

Open `assets/style_config_default.css` and update the variables you want to change:

```css
:root {
  --banner-color: #your-color-here;
  --button-color: #your-color-here;
}
```

- [ ] Open `assets/style_config_default.css` in your repository.
- [ ] Update the color variables you want to change.
- [ ] Commit the change on a new branch and check the pull request preview.

## Change the Navigation Bar

In `_quarto.yml`, change the website title to update the text shown in the navigation bar:

```yaml
website:
  title: "My Website"
```

## Change the Overall Theme

In `_quarto.yml`, set the HTML theme to change the website's overall color scheme and fonts:

```yaml
format:
  html:
    theme: cosmo
```

See the [Quarto HTML themes](https://quarto.org/docs/output-formats/html-themes.html) for available theme options.

## Change the Favicon

1. Create a favicon, for example with [favicon.io](https://favicon.io/favicon-converter/).
1. Replace `resources/images/favicon.ico` with your new file.
1. Check the rendered preview and your browser tab.

## Helpful Color Tools

1. [Venngage Color Accessibility Tool](https://venngage.com/tools/accessible-color-palette-generator)
1. [ColorBuddy](https://color-buddy.netlify.app/)

```{r, echo=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_ottr_footer.md",
  tag_replacement = list(
    "{AUTHORS}" = "Padmashri Saravanan from [BioData Sage](https://www.biodatasage.com/) created the cheatsheet content. Katherine Cox structured OTTR's color customizations. Carrie Wright reviewed the material. Kate Isaac created the original styling, Carrie Wright did the CSS styling, and Carrie Wright and Candace Savonen did the publishing engineering for the cheatsheet."
  ))
```
