---
output:
  html_document:
    includes:
      in_header: ottr_favicon.html
css: css/OTTR_style.css
---

```{r, echo=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_ottr_header.md",
  tag_replacement = list(
    "{TITLE}" = "OTTR Giving Credits",
    "{SUBTITLE}" = "Crediting contributors clearly",
    "{PATH_TO_PNG}" = "https://github.com/ottrproject/cheatsheets/blob/main/pngs/ottr_giving_credits.png?raw=true"
  ))
```

OTTR courses use an `About.Rmd` or `About.md` file to show who contributed to the course and what kind of work they did.

Use the credits table to make contributions easy to understand, especially when the same person appears in more than one role.


## Credits Table Checklist

<input type="checkbox"> Open `About.Rmd` or `About.md` in your course repository.

<input type="checkbox"> Delete rows for optional roles that do not apply to your course (please ensure that you keep rows that credit OTTR developers). 

<input type="checkbox"> Use singular labels for one person and plural labels for multiple people.

<input type="checkbox"> Add links below the table using bracket notation when you want names to link to personal websites. For example:

``` markdown
| Credits | Names |
|:---|:---|
| Lead Content Instructor | [FirstName LastName] |
| Course Publishing Engineers | [FirstName LastName], [SecondName LastName] |

<!-- Author information -->

[FirstName LastName]: https://example.com
[SecondName LastName]: https://example.org
```

## Bracket Notation for Repeated Authors

Bracket notation keeps the credits table readable when a person appears in multiple rows.

Write the person's name in square brackets every place the name should appear:

``` markdown
| Credits | Names |
|:---|:---|
| Lead Content Instructor | [Avery Example] |
| Content Author | [Avery Example], [Sam Rivera] |
| Course Publishing Engineer | [Sam Rivera] |
```

Then link each linked name to their personal website once below the table:

``` markdown
<!-- Author information -->

[Avery Example]: https://avery.example.edu
[Sam Rivera]: https://sam.example.org
```

**The same bracketed name can be reused as many times as needed.** Markdown will link each `[Avery Example]` entry to the same website.


## Instructor Roles

| Role | Use When |
|:---|:---|
| Lead Content Instructor | The person leads the course content and takes on a large share of the teaching/content effort |
| Lecturer | The person delivers the course online or in recorded teaching materials |
| Content Author | The person writes a substantial amount of course content |
| Content Contributor | The person writes a smaller amount of content, less than about one chapter |
| Content Consultant | The person gives specialized content guidance but does not write or edit the content |
| Content Editor | The person edits content without otherwise authoring it |
| Content Director | The person guides the course direction or content strategy |

<p class="comment">
If a person both teaches the material and writes substantial course content, list them in each role that applies.
</p>

## Engineer Roles

| Role | Use When |
|:---|:---|
| Course Publishing Engineer | The person works on the technical setup or generation for this specific course |


:::warning

Ensure the following role allocations are **not** removed from your course:  

| Role | 
|:---|
| Template Publishing Engineer | 
| Publishing Maintenance Engineer |
| Technical Publishing Stylist |
| Package Developer | 
:::

## Art and Design Roles

| Role | Use When |
|:---|:---|
| Illustrator(s) | Created graphics for the course | 
| Figure Artist(s) | Created figures/plots for course | 
| Videographer(s) | Filmed videos | 
| Videography Editor(s)	| Edited film |
| Audiographer(s) |	Recorded audio  | 
| Audiography Editor(s)  | Edited audio recordings | 

```{r, echo=FALSE, results='asis'}
ottrpal::borrow_chapter(
  doc_path = "chunks/create_ottr_footer.md",
  tag_replacement = list(
    "{AUTHORS}" = "Padmashri Saravanan from [BioDataSage](https://www.biodatasage.com/) created the cheatsheet content. Carrie Wright reviewed the material. Kate Isaac created the original styling, Carrie Wright did the css styling and Carrie Wright and Candace Savonen did the publishing engineering for the cheatsheet."
  ))
```
